Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-22 02_Weather.Rmd

# import data from SILO interpolated datasets downloaded from the QLD longpaddock website
silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
silo_king_Tmax <- read.csv("./data/silo_king_Tmax.csv")
silo_gatton_Tmax <- read.csv("./data/silo_gatton_Tmax.csv")
silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")
```

@@

king_Tm_aver[king_Tm_aver$year == "2002" |
                king_Tm_aver$year == "2010" |
                king_Tm_aver$year == "2011" |
                king_Tm_aver$year == "2012" |
                king_Tm_aver$year == "2016",] %>%
   ggplot(aes(x = day)) +
   geom_line(aes(y = max_T, colour = year)) +
   geom_line(aes(y = min_T, colour = year)) +
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
        title = "Maximum and minimum daily temperatures in Kingaroy") +
   scale_x_continuous(
      limits = c(0, 200),
      labels = c(subset(king_Tm_aver, year == 2016)$date[c(1, 50, 100, 150, 200)]),
      breaks = c(1, 50, 100, 150, 200)
   ) +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      xintercept = King_FS$day[1],
      size = 1,
      colour = cols1[1],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[2],
      size = 1.5,
      colour = cols1[2],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[3],
      size = 1,
      colour = cols1[3],
      linetype = "dashed"
   ) +
   geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
   scale_y_continuous(limits = c(0, 40),
                      sec.axis = dup_axis(name = "Rainfall (mm)"))
```

>>>>

# import data from SILO interpolated datasets downloaded from the QLD longpaddock website
silo_war_Tmax <- read.csv("./data/silo_war_Tmax.csv")
silo_king_Tmax <- read.csv("./data/silo_king_Tmax.csv")
silo_gatton_Tmax <- read.csv("./data/silo_gatton_Tmax.csv")
silo_emerald_Tmax <- read.csv("./data/silo_emerald_Tmax.csv")

@@

king_Tm_aver[king_Tm_aver$year == "2002" |
                king_Tm_aver$year == "2010" |
                king_Tm_aver$year == "2011" |
                king_Tm_aver$year == "2012" |
                king_Tm_aver$year == "2016",] %>%

# Create data subset of powdery mildew data means for the first sign of the disease by location
PM.dat_sum <- as.data.frame(do.call(rbind,
                   by(PM.dat, PM.dat$trial_ref, function(x){
                      c(location = unique(as.character(x$location)),
                        year = unique(as.character(x$year)),
                        first_sign = unique(as.character(x$first_sign_disease)),
                        day = as.numeric(unique(sapply(x$first_sign_disease,year2day))))
                   }
                      )), stringsAsFactors = FALSE)

King_FS <- PM.dat_sum[PM.dat_sum$location == "Kingaroy",]
King_FS$day <- as.numeric(King_FS$day)

king_Tm_aver[king_Tm_aver$year == "2002"|
                king_Tm_aver$year == "2010"|
                king_Tm_aver$year == "2011"|
                king_Tm_aver$year == "2012"|
                king_Tm_aver$year == "2016", ] %>%
   ggplot(aes(x = day)) +
   geom_line(aes(y = max_T, colour = year)) +
   geom_line(aes(y = min_T, colour = year)) +
   labs(x = "Date", y = "Daily maximum temperature averaged over 7 days",
        title = "Maximum and minimum daily temperatures in Kingaroy") +
   scale_x_continuous(
      limits = c(0, 200),
      labels = c(subset(king_Tm_aver, year == 2016)$date[c(1, 50, 100, 150, 200)]),
      breaks = c(1, 50, 100, 150, 200)
   ) +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   geom_vline(
      xintercept = King_FS$day[1],
      size = 1,
      colour = cols1[1],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[2],
      size = 1.5,
      colour = cols1[2],
      linetype = "dotted"
   ) +
   geom_vline(
      xintercept = King_FS$day[3],
      size = 1,
      colour = cols1[3],
      linetype = "dashed"
   ) +
   geom_area(aes(y = daily_rain, fill = year), alpha = 0.5) +
   scale_y_continuous(limits = c(0, 40),
                      sec.axis = dup_axis(name = "Rainfall (mm)"))
```
